How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-06-16 Draft_June_2022/Full_draft_20220608.rmd
Added plot for figure 2 across location (commented out) and added regression models plot for pure problem constructions

                                      year), 1, 0))

@@

  mutate(perc=n / sum(n)) %>%

@@

@@

  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation", "Social Economic",
                                            "Sovereign Conservation", 
                                            "Economic Sovereignty", "Social Conservation", "Other")),
         con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),

@@

         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0),

@@

# ama_model$predicted_ei = predict(model_logit_ei, ama_model, type = "response")
# ama_model$predicted_sd = predict(model_logit_sd, ama_model, type = "response")
# ama_model$predicted_sov = predict(model_logit_sov, ama_model, type = "response")

@@

# ama_model_all <- ama_model %>% 
#   pivot_longer(predicted_con:predicted_sov, names_to = "variable", values_to = "value")
# ggplot(ama_model_all, aes(x = km_to_manaus, y = value, color = variable)) +
#   geom_smooth(se = FALSE, size = .5)
ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) + 
  geom_jitter(alpha=.5)+
  geom_smooth(size = .5, color = "darkgreen") +

@@

  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,

@@

       y = "The Amazon as an issue of environmental conservation",
       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance from Manaus",

@@

>>>>

                                      year), 1, 0),
# # Table of Amazonian speeches internationally vs. in Brazil
# amazon_in_out <- pop %>% select(amazon_speech, location_cat)
# table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
# amazon_in_out <- mutate(amazon_in_out,
#                         location_cat = ifelse(grepl("International|Non Identified",
#                                               location_cat), 0, 1))
# amazon_in_out <- table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
# rownames(amazon_in_out) <- c("Not Amazon Speech", "Amazon Speech")
# colnames(amazon_in_out) <- c("Outside of Brazil", "Within Brazil")
# amazon_in_out

@@

  mutate(perc = n / sum(n)) %>%

@@

# # Same plot with location
# perc_in <- pop %>%
#   mutate(location_cat = ifelse(grepl("International|Non Identified", location_cat),
#                                "Outside of Brazil", "Within Brazil")) %>%
#   count(amazon_speech, year, location_cat) %>%
#   mutate(perc = n / sum(n)) %>%
#   filter(amazon_speech == 1) %>% 
#   select(c(perc, amazon_speech, year, location_cat))
# Amazon_year_in <- perc_in %>% ggplot(., aes(x = year, y = perc, fill = location_cat)) +
#   geom_line(aes(color = location_cat)) +
#   geom_text(aes(x = 1988.7, y = 0.34, label = "Chico Mendes"), size = 3) +
#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
#   geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
#   geom_vline(xintercept = c(1988.9, 1992, 2009, 2015),
#              linetype = "dotted") +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
#        color='Y series') +
# Amazon_year_in

@@

  mutate(con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),

@@

         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0))

@@

ama_model$predicted_ei = predict(model_logit_ei, ama_model, type = "response")
ama_model$predicted_sd = predict(model_logit_sd, ama_model, type = "response")
ama_model$predicted_sov = predict(model_logit_sov, ama_model, type = "response")

@@

ama_model_all <- ama_model %>%
  rename("Environmental Conservation" = predicted_con,
         "Economic Integration" = predicted_ei,
         "Social development" = predicted_sd,
         "National Sovereignty" = predicted_sov) %>% 
  pivot_longer('Environmental Conservation':'National Sovereignty',
               names_to = "Construction", values_to = "Share")
ggplot(ama_model_all, aes(x = km_to_manaus, y = Share, color = Construction)) +
  geom_smooth(size = .5) +

@@

  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.4,

@@

       y = "Share of problem construction",
       title = "How is the Amazon constructed as an issue across locations?",

@@

# # Environmental conservation and location
# ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) + 
#   geom_jitter(alpha=.5)+
#   geom_smooth(size = .5, color = "darkgreen") +
#   geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
#   ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
#                     label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
#   labs(x = "Distance from the Amazon (km)",
#        y = "The Amazon as an issue of environmental conservation",
#        title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance from Manaus",
#        subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
#        caption = "Curve in the plot is smoothed using loess method.") +
#           plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
